The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-21 project/paper/output.tex
Few small tweaks to properties section.

The skew-normal was first introduced by \citet{ref-o'hagan} and further
developed by \citet{ref-azzalini}, \citet{ref-gupta}, and \citet{ref-arnold}.
Some of its other basic properties, given by \citet{pewsey}, are

@@

\begin{equation} \label{eq:standard-sn-pdf}
  f(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
\end{equation}

@@

\begin{align*}
  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
\end{align*}

which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
the curve skews to the left, and when $\lambda > 0$, it skews to the right (a
property we will prove in section \ref{subsec:four-properties}).

>>>>

The skew-normal was first introduced by \citet{o'hagan} and was most notably
further developed by \citet{azzalini-1985}. Some of its other basic properties,
given by \citet{pewsey}, are

@@

\begin{equation} \label{eq:standard-sn-pdf}
  f(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
\end{equation}

@@

\begin{align*}
  f(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
\end{align*}

which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
the curve skews to the left, and when $\lambda < 0$, it skews to the right (a
property we will prove in section \ref{subsec:four-properties}).
